Notes on Design and Implementation of Anglican

### 2015-07-26 paper/paper.tex
general expressions in progress

>>>>

The most general form of CPS transformation receives an
expression and a continuation, and returns the expression
in CPS form with the continuation potentially called in multiple
tail positions. General expressions can be somewhat voluntarily
divided into several groups:
\begin{itemize}
	\item binding forms --- \texttt{let} and
		\texttt{loop/recur};
	\item flow control --- \texttt{if}, \texttt{when},
		\texttt{cond}, \texttt{case}, \texttt{and}, \texttt{or} and \texttt{do};
	\item function applications and \texttt{apply};
	\item probabilistic forms --- \texttt{predict},
		\texttt{observe}, \texttt{sample}, \texttt{store}, and \texttt{retrieve}.
\end{itemize}
